Variance reduction for Markov chains via martingale representations

### 2020-05-03 aap/Revision/vr-mcmc-revision-new-new.tex
update

\begin{lem}
\label{lem:v_ergodicity}
 Assume  {\bf (H1)} and {\bf (H2)}. Then for $0 < \gamma < \overline{\gamma}= \min(m / 4L^2,1/L)$, and for any $x \in \rset^d$  it holds
$$
d_V(\delta_xQ_{\gamma}^{n},\pi_\gamma) \leq C\rho^{n}V(x)
$$
with $V(x) = 1 + \|x\|^2$ and constants
$$
C = \left(1+\pi_\gamma(V)\right)\left(1 + \exp{\left(-\frac{m\gamma}{2}\right)}\right)\left(1+\frac{\overline{b}}{(1-\varepsilon)(1-\exp{\left(-\frac{m\gamma}{2}\right)} - \frac{2b}{2+K^2})}\right);
$$

$$
b = \gamma\left(2K_2^2(L+m) + d + m\right); \quad \overline{b} = b\exp{\left(-\frac{m\gamma}{2}\right)} + K^2 + 1; \quad \varepsilon = 2\Phi\left(-K\sqrt{\left(1+\frac{1}{L}\right)\left(1 + 2L\right)}\right); \quad
$$

$$
\rho = \exp\left\{\gamma\left(\frac{m}{2} - 2\frac{2K_2^2(L+m) + d + m}{K^2 + 1}\right)\frac{\log{(1-\varepsilon)}}{\log{(1-\varepsilon)} + \log{(\exp{\left(-\frac{m\gamma}{2}\right)} + \frac{2b}{K^2+2})}}\right\}
$$
where $K_2 > 0$ is from Lemma~\ref{lem:quadratic_behaviour} and $K > 0$ is arbitrary
\end{lem}

>>>>

\begin{lem}
\label{lem:v_ergodicity}
 Assume  {\bf (H1)} and {\bf (H2)}. Then for $0 < \gamma < \overline{\gamma}= \min(m / 4L^2,1/L)$, and for any $x \in \rset^d$  it holds
$$
d_V(\delta_xQ_{\gamma}^{n},\pi_\gamma) \leq C\rho^{n}V(x)
$$
with $V(x) = 1 + \|x\|^2$ and constants
$$
C = \left(1+\pi_\gamma(V)\right)\left(1 + \exp{\left(-\frac{m\gamma}{2}\right)}\right)\left(1+\frac{b\exp{\left(-\frac{m\gamma}{2}\right)} + K^2 + 1}{(1-\varepsilon)(1-\exp{\left(-\frac{m\gamma}{2}\right)} - \frac{2b}{2+K^2})}\right);
$$

$$
b = \gamma\left(2K_2^2(L+m) + d + m\right); \quad \varepsilon = 2\Phi\left(-K\sqrt{\left(1+\frac{1}{L}\right)\left(1 + 2L\right)}\right); \quad
$$

$$
\rho = \exp\left\{\frac{\gamma m}{4}\frac{\log{(1-\varepsilon)}}{\log{(1-\varepsilon)} + \log{(\exp{\left(-\frac{m\gamma}{2}\right)} + \frac{2b}{K^2+2})}}\right\}
$$
where $K_2 > 0$ is from Lemma~\ref{lem:quadratic_behaviour} and $K>0$ is a positive parameter such that 
$$
K^2 > 4\frac{2K_2^2(L+m) + d + m}{m}
$$
\end{lem}
